---
title: "Pre-read material"
author: "Daniel Sabanés Bové"
---

Hello, and thank you for your interest in the `crmPack` workshop at R/Pharma on 30 September 2026.

To help you get the most from the workshop, I would like to ask you to do a few things in preparation.

## Pre-requisites

The workshop is primarily focused on using `crmPack` to design, run and report CRM trials. Whilst I will briefly cover CRM theory - and compare CRM trials to 3 + 3 trials, it's not really *about* CRM, 3 + 3 or first-in-human trials. If you'd like an introduction or refresher, I recommend:

Garret-Meyer E (2006) The continual reassessment method: a tutorial. Clin Trials 3: 57 - 71. doi: [10.1191/1740774506cn134oa](https://journals.sagepub.com/doi/10.1191/1740774506cn134oa).

As `crmPack` is an R package, you'll obviously need access to R and - preferably - RStudio or VScode if you'd like to play around with the package.  The platform (your laptop, online, etc.) you use shouldn't be an issue.

## Software

First, and most importantly, make sure you have the necessary software installed on your laptop or whatever platform on which you plan to follow the workshop.

Check that you have the latest release version of `crmPack` installed.  You can do this by running the following code in R:

```{r}
#| eval: FALSE
packageVersion("crmPack")
```

and you should get 2.1.0 or higher.  If you don't, you can install the latest release version from CRAN with:

```{r}
#| eval: FALSE
install.packages("crmPack")
```

Next, check that JAGS has been installed. The easiest way to do this is to attach the `rjags` package (which is a dependency of `crmPack`, so it should have been installed in the previous step):

```{r}
library(rjags)
```

If you see something similar to the above (in particular, the line reading `Linked to JAGS 4.3.2`), you're good to go. If not, you'll need to install JAGS as well.

Go to [https://sourceforge.net/projects/mcmc-jags](https://sourceforge.net/projects/mcmc-jags) and click the Download button. \[Ignore the ads. Just wait for the download to start - and finish\]

-   Go to your Downloads folder, double click the `JAGS-4.*.*.exe` file and follow the instructions

## Course materials

The workshop materials are available on GitHub at
[github.com/rpact-com/presentation-2026-09-30-rinpharma](https://github.com/rpact-com/presentation-2026-09-30-rinpharma).

## Thank you and see you soon!

Thank you for your attention. I look forward to seeing you at the workshop.

If anything I've written here is unclear, or if you have questions I haven't answered, please do get in touch. 
